---
title: "Movie Review Appendix"
output: html_document
---

```{r include=FALSE}
library(ggplot2)
source("analyze.R")
projection_Rdata_file <- "data/movie_movie_projection.Rdata"
load(projection_Rdata_file)
descriptive_Rdata_file <- "data/projection_descriptions.Rdata"
load(descriptive_Rdata_file)
```

# 1998 & 2000 Analysis
## Node Edge Counts
```{r echo = F}
summary(projection1998)
```

## Degree Distribution
```{r echo = F}
hist(description_1998$degree_dist,
       main = "Degree Distribution",
       xlab = "Degree",
       breaks = 100)
```

## Degree Strength Distribution
```{r echo = F}
hist(description_1998$degree_strength,
       main = "Degree Strength Distribution",
       xlab = "Degree Strength",
       breaks = 100)
```

## Eigenvector Centrality Distribution
```{r echo = F}
hist(description_1998$evcentrality,
       main = "Eigenvector Centrality Distribution",
       xlab = "Eigenvector Centrality",
       breaks = 100)
```

## Transitivity Distribution
```{r echo = F}
hist(description_1998$transitivity,
       main = "Transitivity Distribution",
       xlab = "Transitivity",
       breaks = 100)
```

# 2000 Analysis
## Node Edge Counts
```{r echo = F}
summary(projection2000)
```

## Degree Distribution
```{r echo = F}
hist(description_2000$degree_dist,
       main = "Degree Distribution",
       xlab = "Degree",
       breaks = 100)
```

## Degree Strength Distribution
```{r echo = F}
hist(description_2000$degree_strength,
       main = "Degree Strength Distribution",
       xlab = "Degree Strength",
       breaks = 100)
```

## Eigenvector Centrality Distribution
```{r echo = F}
hist(description_2000$evcentrality,
       main = "Eigenvector Centrality Distribution",
       xlab = "Eigenvector Centrality",
       breaks = 100)
```

## Transitivity Distribution
```{r echo = F}
hist(description_2000$transitivity,
       main = "Transitivity Distribution",
       xlab = "Transitivity",
       breaks = 100)
```

# Compairison of 1998-1999 vs First 2000
## Degree Distribution Compairison
```{r echo = F}
degree_dist_join <- data.frame(year = 1998,
                                   degree = description_1998$degree_dist)
degree_dist_join <- rbind(degree_dist_join,
                              data.frame(year = 2000,
                                         degree = description_2000$degree_dist))
degree_dist_join$year <- as.factor(degree_dist_join$year)

ggplot(data = degree_dist_join, 
       aes(x = log(degree), y=..density.., fill = year)) +
  geom_histogram(position="identity",
                 colour = "black",
                 binwidth=.5,
                 alpha=0.4) +
   xlab("Log(Degree)") +
   ylab("Density") +
   ggtitle("Degree Density Compairison")
```

## Degree Strength Distribution Compairison
```{r echo = F}
degree_strength_join <- data.frame(year = 1998,
                                   strength = description_1998$degree_strength)
degree_strength_join <- rbind(degree_strength_join,
                              data.frame(year = 2000,
                                         strength = description_2000$degree_strength))
degree_strength_join$year <- as.factor(degree_strength_join$year)

ggplot(data = degree_strength_join, 
       aes(x = log(strength), y=..density.., fill = year)) +
  geom_histogram(position="identity",
                 colour = "black",
                 binwidth=.5,
                 alpha=0.4) +
   xlab("Log(Degree Strength)") +
   ylab("Density") +
   ggtitle("Degree Strength Density Compairison")
```

## Eigenvector Centrality Distribution Compairison
```{r echo = F}
evcent_dist_join <- data.frame(year = 1998,
                                   evcent = description_1998$evcentrality)
evcent_dist_join <- rbind(evcent_dist_join,
                              data.frame(year = 2000,
                                         evcent = description_2000$evcentrality))
evcent_dist_join$year <- as.factor(evcent_dist_join$year)

ggplot(data = evcent_dist_join, 
       aes(x = log(evcent), y=..density.., fill = year)) +
  geom_histogram(position="identity",
                 colour = "black",
                 binwidth=.5,
                 alpha=0.4) +
   xlab("Log(Eigenvector Centrality)") +
   ylab("Density") +
   ggtitle("Eigenvector Centrality Density Compairison")
```

## Transitivity Distribution Compairison
```{r echo = F}
transitivity_dist_join <- data.frame(year = 1998,
                                   transitivity = description_1998$transitivity)
transitivity_dist_join <- rbind(transitivity_dist_join,
                              data.frame(year = 2000,
                                         transitivity = description_2000$transitivity))
transitivity_dist_join$year <- as.factor(transitivity_dist_join$year)

ggplot(data = transitivity_dist_join, 
       aes(x = transitivity, y=..density.., fill = year)) +
  geom_histogram(position="identity",
                 colour = "black",
                 binwidth=.1,
                 alpha=0.4) +
   xlab("Log(Transitivity)") +
   ylab("Density") +
   ggtitle("Transitivity Density Compairison")
```